The mid-term impact of COVID-19 on human mobility patterns in Latin American countries

### 2024-01-17 manuscript-3-old/manuscript-latin-countries.qmd
compiling-manuscript

![Maps of population density categories by country with histograms, showing that the distribution of Bing tiles in each density category.](figures/Map_density_histogram.png){fig-align="center" width="625" height="640"}

>>>>

![Maps of population density categories by country with histograms, showing that the distribution of Bing tiles in each density category.](images/Map_density_histogram.png){fig-align="center" width="625" height="640"}
